### 2019-12-09 README.Rmd
update essd ref
typo fix
update doi

[![DOI](https://img.shields.io/badge/DOI-10.5063/F16D5R2B-blue.svg)](https://doi.org/10.5063/F16D5R2B)

@@

## Worflow

@@

Stachelek, J., Ford, C., Kincaid, D., King, K., Miller, H., Nagelkirk, R. (_in prep_) The National Eutrophication Survey: lake characteristics and historical nutrient concentrations.

>>>>

[![DOI](https://img.shields.io/badge/DOI-10.5063/F1CZ35HF-blue.svg)](https://doi.org/10.5063/F1CZ35HF)

@@

## Workflow

@@

Stachelek, J., Ford, C., Kincaid, D., King, K., Miller, H. and Nagelkirk, R., 2018. The National Eutrophication Survey: lake characteristics and historical nutrient concentrations. Earth System Science Data, 10(1), pp.81-86. (https://doi.org/10.5194/essd-10-81-2018)
